% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[stefanos-georgiou]{Stefanos Georgiou}

\thinrule

\startblockquote
{\em On profession}: Passionated with coding, performing experiments,
learning and combining new technologies. {\em On spare-time}: Enjoying
sports, reading books, and going crazy for travelling and food.
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2016-2019 (expected)}
  {\bf PhD, Management Science and Technology}; Athens University of
  Economics and Business

  {\em Thesis title: Energy and Performance Implications for Software
  Development Practices}

  {\em PhD advisors:
  \useURL[url1][https://www2.dmst.aueb.gr/dds/][][Prof.~Diomidis
  Spinellis]\from[url1] and
  \useURL[url2][https://www.balab.aueb.gr/panos-panagiotis-louridas.html][][Prof.~Panos
  Louridas]\from[url2]}
\stopdescription

\startdescription{2013-2015}
  {\bf MSc, Pervasive Computing and Communications for Sustainable
  Development (PERCCOM)}; Erasmus Mundus Joint Master Degree

  ITMO University of Saint-Petersburg (Russia) {\em Thesis title:
  Implementating Green IT Approach for Transferring Big Data over
  Parallel Data Links}; \useURL[url3][msc_thesis.pdf][][Link]\from[url3]

  Lulea University of Technology (Sweden) {\em Semester 3: Resource
  Efficient Pervasive Computing Systems and Communications}

  Lappeenranta University of Technology (Finland) {\em Semester 2: Smart
  Software and Services}

  Unversity of Lorraine (France) {\em Semester 1: Sustainable Computer
  Network Engineering}
\stopdescription

\startdescription{2008-2013}
  {\bf BSc, Networks and Systems Programming}; University of Cyprus

  {\em Thesis title: Implementation and Evaluation of the Biologically
  -- Inspired AntHocNet Routing Protocol in Sensor Network};
  \useURL[url4][bsc_thesis.pdf][][Link]\from[url4]
\stopdescription

\subsection[experience]{Experience}

{\bf Teaching and tutoring:}

Assisting my PhD advisor at Programming II course (Winter Semester of
2017 and 2018). Main responsibilities are giving tutorial and Lab
sessions, guiding students on team assignments and preparing
presentations. Secondary, providing lectures and tutorials for 1st and
2nd BootCamp (Oct. 2017 - May 2018)
\useURL[url5][https://github.com/codeandwork/courses][][Link]\from[url5]

{\bf Proposals writing:}

Assisting Singular Logic's European Project Department for writing
proposals and participating in project's telco meetings.

\subsection[technical-experience]{Technical Experience}

\startdescription{Knowledge}
  {\em Programming Languages:} Bash, Java, Python, C, and C++

  {\em Tools and Practices:} GitHub (Travis CI, Coveralls,
  maven-plugins, GH-pages) Java plug-ings (Code Quality Check,
  maven-docker, JDBC, Reports), Python (Pandas framework, statistics,
  matplotlib, seaborn)
\stopdescription

\startdescription{Projects}
  {\em Measuring Energy Consumption:}
  \useURL[url6][https://github.com/stefanos1316/SEMTs_Comparisson][][Software]\from[url6]
  and
  \useURL[url7][https://stefanos1316.github.io/courses/tools/measuring_energy_consumption_direct_approach-p.html\#/][][Hardware]\from[url7]
  tools

  {\em Programming II website:}
  \useURL[url8][https://github.com/stefanos1316/courses][][Course]\from[url8]

  {\em Rosetta Code Experiement:}
  \useURL[url9][https://github.com/stefanos1316/Rosetta_Code_Research_MSR][][Repository]\from[url9]

  {\em ValidateLinks:}
  \useURL[url10][https://github.com/stefanos1316/validateLinks][][Repository]\from[url10]
\stopdescription

\subsection[research-publications]{Research Publications}

\startitemize
\item
  Conference Publications

  \startitemize[packed]
  \item
    Stefanos Georgiou, Maria Kechagia Panos Louridas, and Diomidis
    Spinellis. What are your programming language's energy-delay
    implications? In 15th International Conference on Mining Software
    Repositories: Technical Track, MSR '18. New York, NY, USA, May 2018.
    Association for Computing Machinery.
    \useURL[url11][https://stefanos1316.github.io/my_curriculum_vitae/GKLS18.pdf][][Link]\from[url11].
  \item
    Stefanos Georgiou, Maria Kechagia, and Diomidis Spinellis. Analyzing
    programming languages' energy consumption: an empirical study. In
    PCI 2017: Proceedings of the 21st Pan-Hellenic Conference on
    Informatics, ACM International Conference Proceeding Series. ACM
    Press, September 2017.
    \useURL[url12][https://stefanos1316.github.io/my_curriculum_vitae/GKS17.pdf][][Link]\from[url12]
  \stopitemize
\stopitemize

\subsection[grands-awards-languages-and-living-abroad]{Grands, Awards,
Languages, and Living Abroad}

\startitemize
\item
  Grands and awards:

  \startitemize[packed]
  \item
    Received best paper awards at the 15th Annual DMST Student
    Conference (2018)
  \item
    Marie Skłodowska-Curie funds, SENECA (2016-2019)
  \item
    Erasmus Mundus Masters Scholarship, PERCCOM (2013-2015)
  \stopitemize
\item
  Human Languages:

  \startitemize[packed]
  \item
    Greek/Hungarian (Native speaker)
  \item
    English (Fluent speaker)
  \item
    Russian/ France (Basic knowledge)
  \stopitemize
\item
  Living Abroad:

  \startitemize[packed]
  \item
    Borned in Gyula, Hungary but grown up in Nicosia, Cyprus.
  \item
    Eating baguettes and drinking wine in Lorraine, France (Winter
    Semester of 2013)
  \item
    Taking many sauna sessions in Lappeenranta, Finland (Summer Semester
    of 2014)
  \item
    Fishing beers from ice-cold lakes in Lulea, Sweden (Winter Semseter
    of 2014)
  \item
    Drinking vodka and eating borsh in Saint-Petersburg, Russia (Summer
    Semester of 2015)
  \item
    Teaching in Athens and visiting islands in Greece (Winter Semester
    of 2016 till now)
  \item
    Visiting Delft, Nethelands for my PhD secondment (Half month of
    Sept. 2017)
  \stopitemize
\stopitemize

\thinrule

\startblockquote
\crlf
Troias 2, ground floor, Room 03 or - Axais & Troizinias, second floor -
Athens, Greece
\stopblockquote

\stoptext
